---
title: "Model Selection"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE,message=FALSE,warning=FALSE,quiet=TRUE,progress=FALSE,fig.align='center')
```

Model Selection in R

```{r}
library(ISLR)
summary(Hitters)
```

There are 59 missing salary values so we will remove these rows before proceeding.

```{r}
Hitters <- na.omit(Hitters)
with(Hitters, sum(is.na(Salary)))
```


Best Subset Selection:

Looks through all possible regression models of all different subset sizes and looks for the best of each size. This produces a sequence of models which is the best sunset for each particular size.


```{r}
library(leaps)
regfit.full <-  regsubsets(Salary ~ . , data = Hitters)
summary(regfit.full)
```


By default the above code will only give us subsets up to size 8.  Let's increase this to 19, or all of the variables.

```{r}
regfit.full <- regsubsets(Salary ~ . , data = Hitters, nvmax = 19)
reg.summary <- summary(regfit.full)
names(reg.summary)
plot(reg.summary$cp, xlab = "Number of Variables", ylab = "Cp")
which.min(reg.summary$cp)
points(10, reg.summary$cp[10], pch = 20, col = "red")
```

We can plot the above in a different method to show us which has the lowest Cp and which variables that this includes.  

In the first plot Black squares are included variables and white ones are not.

In the coefficient method will show us which variables and their coefficients are inclueded in our ten variable model.

```{r}
plot(regfit.full, scale = "Cp")
coef(regfit.full, 10)
```


Forward Stepwise Selection;

Forward Stepwise is a greedy algorithm.  It begins with a model containing no predictors and then adds predictors to the model one at a time.  In particular, at each step, it adds the vaiable that adds the greatest additional improvement to the model.  It does not consider all possible models as best subset does. 
```{r}
regfit.fwd <-  regsubsets(Salary ~ ., data = Hitters, nvmax = 19, method = "forward")
summary(regfit.fwd)
plot(regfit.fwd, scale = "Cp")
```


Model selection Using a Validation Set

Lets make a training and validation set, so that we can choose a good subset model.












